Visualize Non-Euclidean Actors Social Media via Joint Social Relationship Representations, Network Characteristics and Media Sentiments

### 2020-10-23 A-BasicCommom/CVPR2021/cvpr_vision.tex
1. Fix and update template.

  In the film industry, visualizing actor stars' social media for analyzing audience intention towards movies is essential to movie producers.
  However, non-Euclidean social media is hard to analyze, I propose an FC-GRU-CNN architecture, named as \underline{N}on-\underline{E}uclidean \underline{N}et, for social media visualization.
  On the analysis of social media, social relationship representations, network characteristics and media sentiments are key factors.
  FC-GRU-CNN architecture exploits the long-term memory ability of the GRU layer in long sequences of film cast,
  the mapping ability of the CNN layer in retrieving all-pairs shortest path feature of the actors' social relationship,
  and non-linear capability of deep FC layer for movie text sentiments and other characteristics.
  The proposed model accuracy is 14\% higher than Reed \etal's model.

@@

  With the development of social networks, actors' influence of social media is increasing, and the influence of actors' consumption spReeds through social networks,
  and using long-term social network data to study the relationships between all actors, directors, and films remains a challenge.
  It is easy to see that the relationship between box-office and the director, actors, scriptwriters, and producers are often non-linear, that is,
  it is difficult to use linear functions to build box-office prediction models.
  By analyzing the social network characteristics of movie actors, sentiments of movies in Sina Weibo posts, all-pairs shortest path,
  it is easy to get the priority of each characteristic by analysis of feature importance,
  the existing prediction algorithm only makes use of the film metadata, lacks the study on the social network characteristics of the actors,
  though the traditional explanation of the film box-office prediction algorithm is sufficing, however, the prediction accuracy is not satisfactory.
  This paper presents a model, named FC-GRU-CNN, for movie box-office prediction, combining characteristics of film metadata, actors' social network measurement,
  all-pairs shortest path, social network text sentiments, and actors' artistic contribution characteristics,
  as a result, it is 14\% higher in accuracy than Reed \etal ~\cite{reed2016learning}'s model.

@@

  Reed \etal ~\cite{reed2016learning} proposed a CNN-RNN classification model, using CNN layers for extracting the high-order dimensional representation of images,
  and connecting to LSTM layers for description representation, the trained neural network model has accuracy of 56.8\% on Caltech-UCSD Birds dataset and accuracy of 65.6\% on the Flowers dataset.

@@

\section{Representation Learning for Social Relationship, Network Characteristics And artisticContribution}

@@

In summary, randomly choose 10 movies as a test set, as shown in Table 1.
The accuracy of the binary classification model on the training set reached 99.61\%, the accuracy on the test set is 75\%.
Compared to Reed \etal model, see Table 2, the proposed FC-GRU-CNN model converges on the training set and achieves better prediction results on the test set.
Therefore, it can provide decision-making advice in the task of selecting suitable actors for a to-be-cast film,
and in the box-office prediction task, the model can provide reasonable predictions in the market.

@@

\begin{table}
\begin{center}
\begin{tabular}{|l|c|}
\hline
Model & F1-score \\
\hline\hline
Reed \etal  & 61.54\% \\
This paper & 75.0\% \\
\hline
\end{tabular}
\end{center}
\caption{Performance comparison on the models.}
\end{table}

@@

According to the NEN(Non-Euclidean Net) box-office prediction model, this paper discussed the relationship between the movie metadata, Sina Weibo text sentiments, social relationship representations, network characteristics, and actors' artistic contribution in detail.
I proposed an FC-GRU-CNN box-office prediction model, testing on a dataset of $1296$ movies released in China mainland from 2011 to 2015, the model accuracy improves 14\% compared to Reed \etal's model.

{\small
\bibliographystyle{ieee_fullname}
\bibliography{cpvr_movienet}
}

>>>>

  In the film industry, visualizing actor stars' social media for analyzing audience intention towards movies is essential to movie producers.
  However, non-Euclidean social media is hard to analyze, I propose an FC-GRU-CNN architecture, named as \underline{N}on-\underline{E}uclidean \underline{N}et, for social media visualization.
  On the analysis of social media, social relationship representations, network characteristics and media sentiments are key factors.
  FC-GRU-CNN architecture exploits the long-term memory ability of the GRU layer in long sequences of film cast,
  the mapping ability of the CNN layer in retrieving all-pairs shortest path of the actors' social relationship,
  and non-linear capability of deep fully connected layer for movie text sentiments and other characteristics.
  The proposed model accuracy is 14\% higher than Reed \etal~\cite{reed2016learning}'s model.

@@

  With the development of social networks, actors' influence of social media is increasing, and the influence of actors' consumption spReeds through social networks,
  and using long-term social network data to study the relationships between all actors, directors, and films remains a challenge.
  It is easy to see that the relationship between box-office and the director, actors, scriptwriters, and producers are often non-linear, that is,
  it is difficult to use linear functions to build box-office prediction models.
  By analyzing the social network characteristics of movie actors, sentiments of movies in Sina Weibo posts, all-pairs shortest path,
  it is easy to get the priority of each characteristic by analysis of feature importance,
  the existing prediction algorithm only makes use of the film metadata, lacks the study on the social network characteristics of the actors,
  though the traditional explanation of the film box-office prediction algorithm is sufficing, however, the prediction accuracy is not satisfactory.
  This paper presents a model, named FC-GRU-CNN, for movie box-office prediction, combining characteristics of film metadata, actors' social network measurement,
  all-pairs shortest path, social network text sentiments, and actors' artistic contribution characteristics,
  as a result, it is 14\% higher in accuracy than Reed \etal~\cite{reed2016learning}'s model.

@@

  Reed \etal proposed a CNN-RNN classification model, using CNN layers for extracting the high-order dimensional representation of images,
  and connecting to LSTM layers for description representation, the trained neural network model has accuracy of 56.8\% on Caltech-UCSD Birds dataset and accuracy of 65.6\% on the Flowers dataset.

@@

\section{Representation Learning for Social Relationship, Network Characteristics and artisticContribution}

@@

In summary, randomly choose 10 movies as the test set, as shown in Table 1.
The accuracy of the binary classification model on the training set reached 99.61\%, the accuracy on the test set is 75\%.
Compared to Reed \etal model, see Table 2, the proposed FC-GRU-CNN model converges on the training set and achieves better prediction results on the test set.
Therefore, it can provide decision-making advice in the task of selecting suitable actors for a to-be-cast film,
and in the box-office prediction task, the model can provide more accurate predictions in the market.

@@

\begin{table}
\begin{center}
\begin{tabular}{|l|c|}
\hline
Model & F1-score \\
\hline\hline
Reed \etal  & 61.54\% \\
This paper & 75.0\% \\
\hline
\end{tabular}
\end{center}
\caption{Performance comparison on the prediction models.}
\end{table}

@@

According to the box-office prediction model, this paper discussed the relationship between the movie metadata, Sina Weibo text sentiments, social relationship representations, network characteristics, and actors' artistic contribution in detail.
I proposed an FC-GRU-CNN box-office prediction model, tested on a dataset with $1296$ movies released in China mainland from 2011 to 2015, the model accuracy improves 14\% compared to Reed \etal's model.

{\small
\bibliographystyle{ieee_fullname}
%\bibliography{cpvr_movienet}
\begin{thebibliography}{10}

\bibitem{reed2016learning}
Scott Reed, Zeynep Akata, Honglak Lee, and Bernt Schiele.
\newblock Learning deep representations of fine-grained visual descriptions.
\newblock In {\em Learning deep representations of fine-grained visual
  descriptions}, volume 2016-December, pages 49 -- 58, Las Vegas, NV, United
  states, 2016.

\bibitem{fernandez2014we}
Manuel Fern{\'a}ndez-Delgado, Eva Cernadas, Sen{\'e}n Barro, and Dinani Amorim.
\newblock Do we need hundreds of classifiers to solve real world classification
  problems?
\newblock {\em The journal of machine learning research}, 15(1):3133--3181,
  2014.

\bibitem{jiang2018predicting}
Luyao Jiang and Zhengduo Wang.
\newblock Predicting box office and audience rating of chinese films using
  machine learning.
\newblock In {\em Proceedings of the 2018 International Conference on Education
  Technology Management}, pages 58--62, 2018.

\bibitem{quader2017machine}
Nahid Quader, Md~Osman Gani, Dipankar Chaki, and Md~Haider Ali.
\newblock A machine learning approach to predict movie box-office success.
\newblock In {\em 2017 20th International Conference of Computer and
  Information Technology (ICCIT)}, pages 1--7. IEEE, 2017.

\bibitem{zhu2019film}
Huike Zhu and Zhongjun Tang.
\newblock Film box office forecasting methods based on partial least squares
  regression model.
\newblock In {\em Proceedings of the 11th International Conference on Computer
  Modeling and Simulation}, pages 234--238, 2019.

\bibitem{qiu2018microblog}
Xiaoyang Qiu and Tiffany~Ya Tang.
\newblock Microblog mood predicts the box office performance.
\newblock In {\em Proceedings of the 2018 Artificial Intelligence and Cloud
  Computing Conference}, pages 129--133, 2018.

\bibitem{asur2010predicting}
Sitaram Asur and Bernardo~A Huberman.
\newblock Predicting the future with social media.
\newblock In {\em 2010 IEEE/WIC/ACM international conference on web
  intelligence and intelligent agent technology}, volume~1, pages 492--499.
  IEEE, 2010.

\bibitem{jain2013prediction}
Vasu Jain.
\newblock Prediction of movie success using sentiment analysis of tweets.
\newblock {\em The International Journal of Soft Computing and Software
  Engineering}, 3(3):308--313, 2013.

\bibitem{chi2019does}
Jianyu Chi, Enshu Gu, and Kewei Li.
\newblock How does online word-of-mouth impact movie box office: An empirical
  investigation of china.
\newblock In {\em Proceedings of the 2019 International Conference on
  Artificial Intelligence and Computer Science}, pages 730--735, 2019.

\bibitem{joshi2010movie}
Mahesh Joshi, Dipanjan Das, Kevin Gimpel, and Noah~A Smith.
\newblock Movie reviews and revenues: An experiment in text regression.
\newblock In {\em Human Language Technologies: The 2010 Annual Conference of
  the North American Chapter of the Association for Computational Linguistics},
  pages 293--296, 2010.

\end{thebibliography}

}
